---
title: "Final Script"
author: "David Wong"
date: "September 26, 2017"
output: html_document
---

First, we get the data (need a for loop to get these files, though the for loop will be all wrapped up)
Next, we analyze the data and remove highly flourescent wells
Rewrite the data file while keeping certain columns but having removed these highly fluorescent wells
Make sure it's the right format to put into CDD; name it library_CDD
Goes through CDD, comes out ready for analysis
Need a for loop to read through all of the libraries in one folder, output an analysis concatenated in one file

Also, the CDD_input file will be one per library(rbind all of the individual ones)
Next step is looking at outliers in separate file (with library, well number)

##################################MAIN FUNCTION##########################
#If we had the list of all libraries, the for loop would look like this: THIS WORKS
```{r}

all_fluor_read('C:/Users/Davey Wong/Desktop/ARv7 200K Library Plates', execlib, execnames, 'C:/Users/Davey Wong/Desktop/Output Files')

all_fluor_read <- function(directory,libraryshh, libnames, directory_out) {
  
  for (i in 1:length(libraryshh))
  {
    remfile <- data.frame()
    remlist <- list()
    for(j in 1:length(unlist(libraryshh[i])))
    {
     filed <- read_me_in(directory, libraryshh[[i]][j]) #jth element of ith library
     
     if(sum(which(as.numeric(unlist(filed[6])) == 0)) > 0)
     {
       filed <- filed[-c(which(as.numeric(unlist(filed[6])) == 0)),] #Remove 0s
     }
     remifiled <- removefluor(filed, zfluor(filed), 5) #Remove the fluorescent stuff
     remlist <- rep(libraryshh[[i]][j], nrow(remifiled))
     
     remfiled <- as.data.frame(cbind(as.vector(unlist(remlist)), remifiled)) #Make a data frame with first column being the name of the library-jth element
     remfile <- rbind(remfile, remfiled)
     
    }
    setwd(directory_out)
    names(remfile)[1] <- 'Plate Name' 
    outfile <- paste(paste(libnames[i], 'CDD', sep = '_'), 'csv', sep = '.')
    write.table(remfile, row.names = FALSE, file = outfile, sep = ',')
  }
}
##Ok this works (should work if we had all of the files for every)

```
###This function allows user interaction to remove files
```{r}
#Let's have a set list for the library list and the library names
#This is the FULL LIST
execlib <- list(DL,EAM,ES,LC,LCI,LOPAC,LS,MS,NIHII,NPW,SS,TAR,UCLA)
execnames <- c('DL','EAM','ES','LC','LCI', 'LOPAC','LS', 'MS', 'NIHII', 'NPW', 'SS', 'TAR', 'UCLA')
#If I don't have any specific files, I can remove them here
execlib <- missingfiles(execlib, execnames)


missingfiles <- function(lib, names)
{
  misslib = "Not Done"
  missnum = "Not Done"
  
  while(misslib != "Done")
  {
  misslib <- readline(prompt = "From which library would you like to remove a file (LC, LS, UCLAII, LCI, EAM, DL, TAR, SS, MS, ES, NPW, LOPAC, NIHII)? Type 'Done' if you are finished removing files. ")
  if(misslib == "Done")
    break;
  if(length(which(names == misslib)) == 0)
  {
    misslib <- readline(prompt = "From which library would you like to remove a file (LC, LS, UCLAII, LCI, EAM, DL, TAR, SS, MS, ES, NPW, LOPAC, NIHII)? Type 'Done' if you are finished removing files. ")
  }
  cat("You have picked library:", misslib)
  missnum <- readline(prompt = "Which file do you want to remove? Type 'Done' if you are finished removing files. ")
  if(missnum == "Done")
    break;
  
  if(as.numeric(missnum) > length(unlist(lib[[which(names==misslib)]])))
  {
    missnum <- readline(prompt = "Which file do you want to remove? Type 'Done' if you are finished removing files. ")
  }
  
  cat("Removing:", paste(misslib, missnum, sep = '-'))
  lib[[which(names==misslib)]] <- lib[[which(names==misslib)]][-which(lib[[which(names==misslib)]] == paste(misslib, missnum, sep = '-'))]
  }
  return(lib)
}

```





###Make a function to read in the files from one folder
```{r}
# "C:/Users/Davey Wong/Desktop"
read_me_in <- function (directory, library_index) {#directory is folder location of all the files
  file_in <- read.delim(paste(paste(directory, library_index, sep = '/'), 'txt', sep = '.'), header = FALSE, stringsAsFactors = FALSE)
  zframe <- data.frame(file_in[6:389,])
  mynameiswhat <- file_in [5,]
  names(zframe) <-  mynameiswhat
  return(zframe)
}
#abc <- read_me_in("C:/Users/Davey Wong/Desktop/ARv7 200K Library Plates", 'NPW-1')
#head(abc)
#names(abc)[25]



#head(removefluor(abc, zfluor(abc), 5))
#execlib
#execnames
```





###Make a function to compute z-scores of fluorescent levels compared to columns 2 and 23 Good to go
```{r}

zfluor <- function(x){#x here is the read-in file
  z_list <- list()
  aver_intens <- mean(as.numeric(unlist(x[26]))[c(17:32, 353:368)])
  sd_intens <- sd(as.numeric(unlist(x[26]))[c(17:32, 353:368)])
  for(i in 1:length(as.numeric(unlist(x[26])))){
    z_list[i] <- (as.numeric(unlist(x[26]))[i] - aver_intens)/sd_intens 
  }
  return(as.vector(z_list))
}



```





###Function that removes fluorescent wells (higher than threshold (maybe just higher and not below z-score)) Good to go
#Also want to remove wells with 0 in it (check each column if it is 0)
```{r}
removefluor <- function(file, x, crit) {#x here will be a zfluor output
  remdata <- unlist(x)
  if(sum(x > 5, na.rm = TRUE) == 0 )
  {
    return (file[,c(which(names(file)=="Well Name") ,4,26,27,32,33)])
  }
  else 
  {
    remdat <- file[-(which(remdata > crit)),  c(which(names(file)=="Well Name"),4,26,27,32,33)]
    names(remdat) <- names(file)[c(which(names(file) == "Well Name"),4,26,27,32,33)]
  
  }
  return(remdat)
}
#names(abc)
#which(as.numeric(unlist(removefluor(abc, zfluor(abc), 5)[6])) == 0)
#abcrm <- removefluor(abc, zfluor(abc), 5)


#sum(which(as.numeric(unlist(abcrm[6])) == 0)) > 0
#abcrm
#head(removefluor(read_me_in('C:/Users/Davey Wong/Desktop/ARv7 200K Library Plates', 'NPW-1'), zfluor(read_me_in('C:/Users/Davey Wong/Desktop/ARv7 200K Library Plates', 'NPW-4'))))

#names(read_me_in('C:/Users/jklee/Desktop/ARv7 200K Library Plates', 'NPW-1'))
```
#Making the library of library names (May have to remove some of the names if the files for them don't exist)
```{r}
write_lib <- function(x, plate, number)
{
  for(i in 1:number)
  {
    x[i] <- paste(plate, i, sep = '-')
  }
  return(x)
}


LC <- list()
LC <- unlist(write_lib(LC, 'LC', 158))
LS<- list()
LS <- unlist(write_lib(LS, 'LS', 125))
UCLA <- list()
UCLA <- unlist(write_lib(UCLA, 'UCLA',94))
LCI <- list()
LCI <- unlist(write_lib(LCI, 'LCI', 73))
EAM <- list()
EAM <- unlist(write_lib(EAM, 'EAM', 63))
DL <- list()
DL <- unlist(write_lib(DL, 'DL', 62))
TAR <- list()
TAR <- unlist(write_lib(TAR, 'TAR', 27))
SS <- list()
SS <- unlist(write_lib(SS, 'SS', 8))
MS <- list()
MS <- unlist(write_lib(MS, 'MS', 7))
ES <- list()
ES <- unlist(write_lib(ES, 'ES', 6))
NPW <- list()
NPW <- unlist(write_lib(NPW, 'NPW', 4))
LOPAC <- list()
LOPAC <- unlist(write_lib(LOPAC, 'LOPAC', 4))
NIHII <- list()
NIHII <- unlist(write_lib(NIHII, 'NIHII', 3))
```

